\section{Outline}
\label{sec:intro_outline}

\begin{enumerate}
  \item \textbf{Background} (\Cref{ch:background}) \textemdash\ Describing access control \& encryption and the reliance on public key infrastructures for \textit{asymmetric} encryption. Presenting the requirements of resource servers and the capabilities of the \OpenABE \& \PyOpenABE libraries.
  \item \textbf{Analysis/Requirements} (\Cref{ch:analysis}) \textemdash\ The security \& deployment considerations for the \theResServer system. Analysis of the requirements for enrolling into the system and the Case Studies for the \acrshort{dcs} deployment scenario.
	\item \textbf{Design} (\Cref{ch:design}) \textemdash\ Presentation of the design of the \thePolicyLang language including a formal language definition and the process for signing \& issuing user keys with consideration for the deployment scenario. How users can build policies and search across filenames on the \acrfull{prs}, with presentation of the \theResServer system architecture.
	\item \textbf{Implementation} (\Cref{ch:implementation}) \textemdash\ Integrating with the \OpenABE toolset and choosing Python's Flask for web servers. Discussion of the Client server security, the decision to store data with mongoDB and providing a fuzzy string matching service for filenames.
	\item \textbf{Evaluation} (\Cref{ch:evaluation}) \textemdash\ Presenting the security evaluation \& risk assessment, along with a discussion of features that were successfully achieved and addressing those that the project failed to achieve.
	\item \textbf{Conclusion} (\Cref{ch:conclusion}) \textemdash\  Summary of the project with a discussion of future work that would add additional functionality to the \theResServer system.
\end{enumerate}
